Composition-climate paper

### 2015-06-24 Composition_Ecology.Rmd
Pushing changes to the structure of the code.  I've been writing all the `source`d files as functions so that there's not as much information in the global environment to worry about causing bugs.
* moved `RColorBrewer` into the setup file.

* Moved `best.taxa` up into a global variable.

* Naturalearth is a function, returns a list.

* `resample_climate` returns a value, it's all wrapped into a function.

* `climate_boxplots` becomes a function (`clim_boxplots`).

* `climate_ts` is now a function.  Returns three tables.

* `get_loss_gain` makes a function that exports the panel plot.

@@

base_map <- natural_earth()

@@

changes <- modern$value - past$value
```
**Figure 1**. *Climate change in the Upper Midwest over the last two centuries using PRISM data and North American Drought Atlas PDSI reconstructions.  Low temperatures in the 1970s result in lower T_max_ during the modern era, but climate change has resulted in higher T_min_ values than the early-century normals, along with increasing A_ppt_.  PDSI shows strong coherence with A_ppt_ in this region.*

@@

@@

source('R/resampling_climate.R')

source('R/figures/climate_boxplots.R')

boxplot_clim

>>>>

best.taxa <- c('beech', 'ironwood', 'hemlock', 'fir', 'cedar.juniper', 
              'basswood', 'spruce', 'elm', 'ash', 'pine', 'oak', 
              'tamarack', 'maple', 'poplar', 'birch')

@@

natural <- natural_earth()

@@

climate_values <- climate_ts(unit.raster, pls_data, climate$now, climate$then)

changes <- climate_values$modern$value - climate_values$past$value

```
**Figure 1**. *Climate change in the Upper Midwest over the last two centuries using PRISM data and North American Drought Atlas PDSI reconstructions.  Low temperatures in the 1970s result in lower T_max_ during the modern era, but climate change has resulted in higher T_min_ values than the early-century normals, along with increasing A_ppt_.  PDSI shows strong coherence with A_ppt_ in this region.*

@@

loss_plots <- loss_plot()

@@

source('R/resampling_climate.R')
vegclim_table <- resample_climate(climate, agg_dens, pls_data)

source('R/figures/climate_boxplots.R')
boxplot_clim <- clim_boxplots(clim_table = vegclim_table)
boxplot_clim
